---
title: "Simulation Modeling in Immunology (SMI)"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
 
```



<!-- Some trickery to get the logo to show -->
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"media/smi_logo.png\" style=\"float: right; border: none; width: 150px;\"/>')
   });
</script>

Last update/recompile: `r Sys.time()`

Welcome to the website **Simulation Modeling in Immunology (SMI).** 

This website is a repository of materials covering infectious diseases and immunology, with a focus on modeling.

This resource was developed and is maintained mainly by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html) (see below for further contributors). 
We use some of the materials on this website for our annual course _Infectious Diseases, Immunology and Within-Host Models_ which is part of the [Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID)](https://si.biostat.washington.edu/suminst/sismid). We also use the materials for other workshops we occasionally teach on this topic. 
We keep this website continuously online, with updates happening every time we teach a course - or if we have otherwise time and reason to update things `r emoji::emoji('smiley')`.


# Website content

The __Overview__ section provides a very brief overview.

The __Immunology__ and __Modeling__ sections and subsections contain the bulk of the content. The various sections generally consist of a mix of embedded videos, slides, some code an longer write-ups.

The __Glossary__ section provides a (work in progress) glossary with definitions of technical terms.

The __Resources__ section contains a listing of external materials that might be of interest for further learning of the topics covered on this site. 


# Notes

By default, all links open in the current tab. You'll likely want external ones to open in a separate tab or window. To do so, you can (with most browsers) hold the `Ctrl` button when clicking, or do a right-click and select `open in new tab/window`.


# Contribute

**We welcome contributions in the form of feedback, suggestion for edits/additions, etc. You can either [contact us](https://www.andreashandel.com/), file a GitHub Issue, or contribute through a pull request.


# Acknowledgements

This course was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("SMICoursecontributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```


# License

The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](https://creativecommons.org/licenses/by-nc-sa/4.0/) Linked and embedded materials are governed by their own licenses. I assume that all external materials used or embedded here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and I will remove it. 


  
