---
title: "Simulation Modeling in Immunology"
output: 
  html_document:
    toc: FALSE
---

```{r, include = FALSE}
#just so I can use emoticons
#devtools::install_github("hadley/emo")
library(emo)
```


Welcome to the website **Simulation Modeling in Immunology (SMI).** 

This website is the main resource for the course/module called [Infectious Diseases, Immunology and Within-Host Models](https://si.biostat.washington.edu/suminst/sismid2020/modules/MD2010), which is part of the [Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID)](https://si.biostat.washington.edu/suminst/sismid). The course is taught by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html). 

We plan to keep this website continuously online, with updates happening every time we teach the course again - or if we have otherwise time and reason to update things `r emo::ji('smiley')`.


# Important Notes

**1. The website should now be functional. We'll likely keep adding material throughout the course, so check often. If you see anything not working, let us know or fix it yourself `r emo::ji('smiley')` (see under _Contribute_ below).**

**2. Some of the binaries for DSAIRM version 0.8.6 still don't seem to be on CRAN. First, if things don't work, please upgrade to the latest version of R and update all your packages. If after that you still can't install 0.8.6 using `install.packages('DSAIRM')`, you can try to download the package zip file `DSAIRM_0.8.6.tar.gz` [from here](https://cloud.r-project.org/web/packages/DSAIRM/index.html) and in RStudio in the bottom right window go to `Packages` then `Install` and choose `Package Archive File`. You can also install from Github. To do so, first install the `remotes` package with `install.package('remotes')`, then install from Github with `remotes::install_github('ahgroup/DSAIRM')` As last backup, you can use the online version: https://shiny.ovpr.uga.edu/DSAIRM/**

**3. We will record all Zoom sessions. They will be made available to you. We would also like to post them publicly to this website. If you have concerns about that, please let us know. Otherwise we assume you are ok with us posting those recordings.**

```{r, include = FALSE}
#**3. Everyone should have received an invite to the SMI-2020-course Slack workspace. If you haven't let me (Andreas) know.**
```

# More Notes

We hope this is not too confusing, but we call every unit in our course a _Module_. So this course is a SISMID module, but in our terminology, we call this whole "thing" the _course_ or _class_, and use _module_ for individual segments, which are further divided into _units_.

By default, all links open in the current tab. You'll likely want external ones to open in a separate tab or window. To do so, you can (with most browsers) hold the `Ctrl` button when clicking, or do a right-click and select `open in new tab/window`.


# Website content

The __General Information__ section provides a  __Syllabus__ and a __Schedule__. 


The majority of the content is listed under the __Modules__ heading. Each module has several units in a drop-down/pop-out menu. Go through them in the listed order.

You have the opportunity to do an optional project. Instructions and detailed information for this are given in the __Project__ section.

The __Communication__ section provides information on how course communications are planned to happen.

The __Resources__ section contains a listing of external materials. The _Course Resources_ page lists materials used in this course. The _General Resources_ page lists additional materials that are relevant to the course topic and might be of interest. 

The __Glossary__ section provides a (work in progress) glossary with definitions of technical terms.


# Getting started

Start by looking over the __Syllabus__ and __Schedule__ documents, then __Communication__ and __Resources__. After that, start with the __Module 1__ content in the given order. 


# Contribute

**We welcome contributions in the form of feedback, suggestion for edits/additions, etc. You can either tell us or you can even contribute directly through a GitHub pull request.** (If you don't know what a GitHub pull request is and how you can do that, see the GitHub specific instructions [here](https://andreashandel.github.io/MADAcourse/Exercise_Tidyverse.html). You can ignore the part that talks about the `tidyverse`. You might also want to check out [this brief GitHub introduction](https://andreashandel.github.io/MADAcourse/1d_Github.html)).


# Acknowledgements

This course was developed and is maintained by [Andreas Handel](https://www.andreashandel.com/) and [Paul Thomas](https://www.stjude.org/directory/t/paul-thomas.html).

```{r, results = "asis", echo = FALSE, message = FALSE, warning=FALSE}
#the following code snipped is taken from Hadley's R4DS intro page
library(dplyr)
contributors <- readr::read_csv("SMICoursecontributors.csv", col_types = list())
contributors <- contributors %>% 
  mutate(
    link = glue::glue("[\\@{GithubID}](https://github.com/{GithubID})"),
    desc = ifelse(is.na(LastName), link, glue::glue("{FirstName} {LastName} ({link})"))
  )
cat("The following individuals have contributed to improving the course:\n")
cat(paste0(contributors$desc, collapse = ", "))
```


# License

The materials are licensed under the [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.](https://creativecommons.org/licenses/by-nc-sa/4.0/) Linked and embedded materials are governed by their own licenses. I assume that all external materials used or embedded here are covered under the educational fair use policy. If this is not the case and any material displayed here violates copyright, please let me know and I will remove it. 


  
